---
title: "R Notebook"
output: html_notebook
---
Problem 1.

import the dataset
```{r}
winemag <- read.csv("~/Downloads/wine-reviews/winemag-data_first150k.csv", stringsAsFactors=FALSE)
```

1. Plot histogram of price. (10 points)
```{r}
summary(winemag$price)
require(ggplot2)
ggplot(winemag, aes(x=price)) + xlim(c(0,1500)) + geom_histogram(binwidth=20) + ggtitle("The historgram of price")
```

2. Plot histogram of points. (10 points)
```{r}
ggplot(winemag, aes(x=points)) + geom_histogram(binwidth=.5) + ggtitle("The historgram of points")
```

3. Create a dataframe with country, variety, average value of points and average value of
price.
```{r}
require(dplyr)
df_3 <- winemag %>% group_by(country,variety) %>% summarize(avgPoints = mean(points,na.rm=TRUE),avgPrice = mean(price,na.rm=TRUE))
head(df_3)
```

4. Arrange the above dataframe in descending order of points. Plot heatmap considering
first 10 values of the arranged dataframe. The x axis of heat map should have countries,
y axis should have variety, and the heat map should be filled with values of average
points (10 points)
```{r}
df_4 <- df_3 %>% arrange(desc(avgPoints)) %>% head(10)
ggplot(df_4,aes(x=country,y=variety))+geom_tile(aes(fill=avgPoints)) + ggtitle("heatmap: variety and country and average points")
```

5. Is there a relationship between average price and average points. Compute the Pearson
correlation coefficient. Plot a scatter plot with average points on x axis and average
price on y axis. Fit a linear model and compute the values of slope and intercept. (20
points)
```{r}
peaCorr <- cor.test(x=df_3$avgPoints, y=df_3$avgPrice, method = 'pearson')
peaCorr
ggplot(df_3, aes(x=avgPoints, y=avgPrice)) + geom_point() + geom_smooth(method=lm) + ggtitle("average points vs average price")
fit = lm(formula = df_3$avgPrice ~ df_3$avgPoints)
fit
```

6. Does a winery offering more variety of wines attract more points on average? Is there
a trend between variety and average points? (10 points)
```{r}
df_6 <- winemag %>% group_by(winery) %>% summarize(cntVariety = n_distinct(variety), avgPoints = mean(points,na.rm=TRUE))
ggplot(df_6, aes(x=cntVariety, y=avgPoints)) + geom_point() + geom_smooth(method=lm) + ggtitle("variety vs points")
cor(as.numeric(df_6$cntVariety),as.numeric(df_6$avgPoints))
```
Jugding by the graph and correlation, there is no relationship between the variety and average points.


Problem 2.

1. An example is shown below. The left part of figure is a sample edgelist. The right part
is the corresponding Adjacency matrix. Similar to the example shown below convert
the data given in edgeleist.csv into an Adjacency matrix. Your solution will be a 17x17
matrix. (10 points)
```{r}
require(igraph)
edgelist <- read.csv("~/Downloads/edgelist.csv", stringsAsFactors=FALSE)
egraph <- edgelist[c(2,3)] %>% graph_from_data_frame()
as.matrix(get.adjacency(egraph))
```

2. Use the adjacency matrix created above and convert it to a network object using igraph
package. Plot the network showing all the node labels. (10 points)
```{r}
V(egraph)$size <- 25
simplify(egraph) %>% plot(edge.arrow.size=.4, edge.curved=.1)
```

3. Add a node (vertex) attribute and name it as type. Assign value A to nodes S01 to
s08, value B to nodes S09 to s14, and value C to nodes S15 to s17. Plot the network
showing all node labels and color node by type attribute. (10 points)
```{r}
V(egraph)$type[V(egraph)$name %in% c("s01","s02","s03","s04","s05","s06","s07","s08")] <- "A"
V(egraph)$type[V(egraph)$name %in% c("s09","s10","s11","s12","s13","s14")] <- "B"
V(egraph)$type[V(egraph)$name %in% c("s15","s16","s17")] <- "C"
col <- c("gray50", "tomato", "gold")
V(egraph)$color <- col[factor(V(egraph)$type) %>% as.numeric()]
simplify(egraph) %>% plot(edge.arrow.size=.4, edge.curved=.1)
```

4. Plot the network showing all nodes such that the node sizes are varied according their
respective degrees. (10 points)
```{r}
deg <- degree(egraph,mode="all")
V(egraph)$size <- deg*3
V(egraph)$color <- "white"
simplify(egraph) %>% plot(edge.arrow.size=.4, edge.curved=.1)
```





